### 2018-05-10 Main.Rmd
Created basic igraph from assoc_pairs.

#Make list of pairs for associative data
#The output: all pairs of words (first is named "item"" and seoncd is named "pair"), link =0 (no link), =1 (there is a link)
assoc_pairs<- make_assoc_pairs(lemma_list = lemma_list)

@@

>>>>

#Make list of pairs for associative data
#The output: all pairs of words (first is named "item"" and second is named "pair"), link =0 (no link), =1 (there is a link)
assoc_pairs <- make_assoc_pairs(lemma_list = lemma_list)

@@

```{r}
lemma_vertices <- lemma_list %>%
  rename("name"="item")

assoc_links <- assoc_pairs %>%
  filter(link==1) %>%
  select(item, pair, item.definition, pair.definition) %>%
  rename("from"="item", "to"="pair")

g <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>% simplify()
print(g, e=TRUE, v=TRUE)
```
